### 2019-04-24 sections/semantics.tex
convert back to two column layout
rename main tex file to main
fixed typo

\begin{figure}[h]
  \centering
  \includegraphics[width=0.6\columnwidth,page=5]{figures/drawings-crop.pdf}
  \caption{
    Semantic functions defined in this report and their relation.
  }
  \label{fig:semantic-functions}
\end{figure}

@@

Also, we mad an implementation of \TOPHAT combinators into \ITASKS,
so that \TOPHAT specifications can be compiled to runnable applications.
This shows that \TOPHAT is a subset of \ITASKS.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth,page=5]{figures/drawings-crop.pdf}
  \caption{
    Semantic functions defined in this report and their relation.
  }
  \label{fig:semantic-functions}
\end{figure}

@@

Also, we made an implementation of \TOPHAT combinators into \ITASKS,
so that \TOPHAT specifications can be compiled to runnable applications.
This shows that \TOPHAT is a subset of \ITASKS.
